### 2021-05-31 paper/model/summary.tex
Update Readme and add pdf.
Update model summary.

To predict the effects of a wide variety of fine-grained social distancing policies
we propose a different model structure.
Our model inherits many features from agent-based simulation models but replaces
the contacts between moving particles by contacts between individuals who work,
go to school, live in a household and enjoy leisure activities.
The structure of the model is depicted in Figure~\ref{fig:model_graph}.

@@

@@

Our model also allows the evaluation of different testing strategies by having a detailed
three-step model of test demand, allocation and processing:
First, individuals demand a test because they, e.g., experience symptoms.
Secondly, tests are allocated to individuals while respecting governmental access
restrictions to test.
Thirdly, depending of the capacities of laboratories, tests are processed for some time
until the individual receives her test result.

In addition, people who have symptoms, received a positive test, or had a risk contact
can reduce their number of contacts across all contact types endogenously.

>>>>

To predict and quantify the effects of a wide variety of fine-grained social distancing policies, vaccinations and rapid testing, we propose a different model structure. Our
model inherits many features from prototypical agent-based simulation models but
replaces the contacts between moving particles by contacts between individuals who work,
go to school, live in a household and enjoy leisure activities.

The structure of the model is depicted in Figure~\ref{fig:model_graph}.

@@

The infection probabilities of contacts vary with contact type, age of the susceptible
person, and the virus strain of the infected person. Moreover, they follow a seasonal
pattern. The strength of the seasonality effect is higher for contacts that are easy to
be moved to an outside location in summer (such as leisure contacts) and smaller for
contacts that take place inside even in summer (e.g. work contacts).

@@

After rapid tests become available, people who work or go to school can receive rapid
tests there. Moreover, people can decide to make a rapid test if they develop symptoms,
have many planned contacts or observe cases in their contact network. People who have a positive rapid test demand a confirmatory PCR test with a certain
probability. Moreover, PCR tests can be demanded because of symptoms or randomly.

This rich model of PCR and rapid tests leads to a share of detected cases that varies
over time and across age groups. It also allows to quantify the effect of changes in
testing policies on the dynamic of infections.

People who have symptoms, received a positive test, or had a risk contact
can reduce their number of contacts across all contact types endogenously. The extent to
which this is done is calibrated from survey data.
